quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-05 paper-quollr.Rmd
Add script with additinal functions

```{r}
# Plot MSE

plot_mse <- function(error_df) {

  ggplot(error_df,
         aes(x = a1,
             y = MSE,
             colour = method)) +
    geom_point(size = 0.8) +
    geom_line(linewidth = 0.3) +
    scale_y_log10() +
    ylab("log(MSE)") +
    xlab(expression(paste("binwidth (", a[1], ")"))) +
    theme_minimal() +
    theme(panel.border = element_rect(fill = 'transparent'),
          plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
          axis.ticks.x = element_line(),
          axis.ticks.y = element_line(),
          legend.position = "none",
          axis.text.x = element_text(size = 7),
          axis.text.y = element_text(size = 7),
          axis.title.x = element_text(size = 7),
          axis.title.y = element_text(size = 7))

}

>>>>

```{r}
#| label: import-scripts
source("scripts/additional_functions.R")
```
